---
title: "Bookstuff"
author: "David Duong"
date: "2024-04-27"
output: html_document
---

```{r setup}
# Add your library below.

library(shiny)

```

## R Bookstuff

The bookstuff function creates a shiny app that lets you add,remove, import and export book data to a csv file.

```{r, bookstuff}
bookStuff <- function() {
  
  ui <- fluidPage(
    titlePanel("Bookshelf"),
    sidebarLayout(
      sidebarPanel(
        fileInput("file",
                  label = "Upload a CSV file",
                  multiple = FALSE,
                  accept = c(".csv"),
                  buttonLabel = "Upload"),
        textInput("title", "Book Title"),
        textInput("author", "Author"),
        selectInput("status", "Status", choices = c("Finished", "Currently Reading", "To Be Read")),
        actionButton("addBtn", "Add Book"),
        actionButton("removeBtn", "Remove Book"),
        actionButton("exportBtn", "Export to CSV")
      ),
      mainPanel(
        dataTableOutput("bookTable")
      )
    )
  )
  
  server <- function(input, output, session) {
    # Initialize reactiveValues to store books
    rv <- reactiveValues(books = data.frame(Title = character(), Author = character(), Status = character(), stringsAsFactors = FALSE))
    
    # load csv file
    observeEvent(input$file, {
      
      rv$books <- read.csv(input$file$datapath)
    })
    
    # Add Book button 
    observeEvent(input$addBtn, {
      author <- input$author
      title <- input$title
      status <- input$status
      new_book <- data.frame(Author = author, Title = title, Status = status, stringsAsFactors = FALSE)
      rv$books <- rbind(rv$books, new_book)
    })
    
    # Remove Book button 
    observeEvent(input$removeBtn, {
      title_to_remove <- input$title
      rv$books <- rv$books[rv$books$Title != title_to_remove, ]
    })
    
    # Export to CSV button 
    observeEvent(input$exportBtn, {
      write.csv(rv$books, 'books.csv', row.names = FALSE)
    })
    
    # print df
    output$bookTable <- renderDataTable({
      rv$books
    })
  }
  
  shinyApp(ui = ui, server = server)
}
```

## How to Use

The function lets you input author, title information as well as categorized them based on whether the book is finished, reading, or to be read. It also has the option export the list as a csv or you can also import your own list instead of starting a new one. I provided a sample list within the data folder to try.


```{r, example}
bookStuff()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
